Geometrization of characters of tori over non-Archimedean local fields

### 2013-07-12 shanghai.tex
Added \text to the \GxG style commands to prevent LaTeX from messing with spacing; changed implementation slightly

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Geometration of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{manfnt}

@@

@@

\newcommand{\tighttimes}{\hskip-1pt\times\hskip-1pt}
\newcommand{\tightertimes}{\hskip-3pt\times\hskip-3pt}
\newcommand{\tighterboxtimes}{\hspace{-2pt}\boxtimes\hspace{-2pt}}

\renewcommand{\bf}{\bar{f}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bm}{\bar{m}}
\newcommand{\bG}{\bar{G}}
\newcommand{\bH}{\bar{H}}
\newcommand{\GxG}{G \tightertimes G}
\newcommand{\bGxG}{\bar{G} \tightertimes \bar{G}}
\newcommand{\bfxf}{\bar{f} \tightertimes \bar{f}}
\newcommand{\GxxG}{G \tighttimes G}
\newcommand{\LxL}{\gcs{L} \tighterboxtimes \gcs{L}}

@@

  \[
  \xymatrix{
    \bm_3^*\gcs{L} \ar[rr]^{(\bm\times \id)^*\mu} \ar[d]_{(\id\tightertimes \bm)^*\mu}
    &&  \bm^*\LxL \ar[d]^{\mu \boxtimes \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]
    &&  \gcs{L} \boxtimes\LxL\\
  }
  \]
  commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;

@@

  \[
  \xymatrix{
    \Frob_{\GxxG}^* \bm^* \gcs{L} \ar[rr]^{\Frob_{\GxxG}^*\mu}
    && \Frob_{\GxxG}^*(\LxL)\\
    \ar@{=}[u] \bm^*  \Frob_{G}^* \gcs{L} \ar[d]_{\bm^* F}
    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
    \bm^*\gcs{L} \ar[rr]^{\mu}
    && \LxL\\
  }
  \]
  commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such then
  \[
  \xymatrix{
  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
  && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
  }
  \]
  both commute.
\end{enumerate}

@@

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
determines a point $\bg$ on $\bG$ fixed by $\Frob_G$ and
therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically (this
follows from second condition appearing in the definition of character
sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
defined by $g \mapsto F_{\bg}$, is a group homomorphism;
we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
  $1$ local system. More generally, trace is needed.}

@@

  To see that $(\bfxf)^* \gcs{L}$ satisfies
  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \boxtimes \bf^*\gcs{L}$
  (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
  Then use the fact that $f$ is defined over $\Fq$, so
  $(\bfxf)^*\Frob_{\GxxG}^* \iso \Frob_{\GxxG} (\bfxf)^*$,
  and the fact that $f$ is a morphism of group schemes, so
  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
  (isomorphisms of functors on constructible sheaves).

  To see that $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
  $\bf^*\tightertimes\bf^*$ to \ref{CS.3} and argue as
  above. It follows from the fact that sheaf hom commutes with these
  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

@@

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  \Clifton{Agreed. I'll do that.}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

  Let us review how line bundles on $G^0$ determine character sheaves
  on $G^0$.  Up to isomorphism, line bundles on $G^0$ may be
  apprehended in terms of pairs $(\pi,\psi)$,
  \David{Aren't there line bundles which are not character sheaves,
    for which $B$ is not an algebraic group?}
  where $\pi : B\to G^0$ is a finite etale morphism of algebraic
  groups and a character $\psi : A\to \EEx$, where
  $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as
  summarized by the following diagram.
  \begin{equation}\label{E}
    \xymatrix{
      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
      }
  \end{equation}
  (In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the
  Lang isogeny for $G^0$.)  Indeed, $\cs{E}$ is precisely the
  component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$.  To
  see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back
  $\pi: B \to G^0$ along $m_0 : G^0\times G^0 \to G^0$.
  \begin{equation}
    \xymatrix{
      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
      & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] A\times A  \ar[r]
      & \ar[u]^{m_{B}} B\times B \ar[r]^{\pi\tighttimes \pi}  & \ar[u]^{m_0} G^0\times G^0 \ar[r] & 1\\
      }
  \end{equation}
  As pictured above, the kernel of this pull-back is $A\times A$;
  indeed, $A\times A\to B\times B$ is the pull-back of $A\to B$ along
  $m_{B}$. Use this Cartesian square to define a character (the dotted
  arrow, above) of $A\times A$; that is, define $A\times A\to \EEx$
  by the composition of $A\times A \to A$ and $\psi : A\to \EEx$.
  Note that this character is $\psi \otimes \psi : A\times A\to \EEx$.
  \Clifton{I haven't explained how maps between diagrams define sheaf
    homomorphisms between local systems.}
  Since the lower sequence is precisely the sequence defining
  $\cs{E}\boxtimes\cs{E}$, this shows that, by construction, $\cs{E}$
  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \cs{E}\boxtimes\cs{E}$.
  Now the base change $\cs{E}$ comes equipped with isomorphisms
  $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
  $\mu^0 : \bm_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$
  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
  is a character sheaf of $G^0$.

@@

  Observe that $\bm: \bG\times \bG\to \bG$ is
  completely determined by the family of maps
  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
  for all $x,y\in X$. To do that, note first that the local system
  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
  \[
  \xymatrix{
    \EEx && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
    }
  \]
  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
  the result is the middle horizontal diagram below, where we use the
  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
  \[
  \xymatrix{
    & \ar[dl]_{\psi_{x+y}} \Aut(\bf^{x+y})
    & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
    \EEx & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
    & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
    && \ar[u]_{\bm_{x,y}} \bG^x\times \bG^y\\
    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \ar[u] \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y}
    && \ar@{=}[u] \bG^x\times \bG^y\\
    }
  \]
  Now, the homomorphism from the covering group of
  $\bf^x\times\bf^y$ to the covering group of
  $\bf^{x+y}$ induced by the composition
  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
  Since this map commutes with the characters $\psi_x\otimes\psi_y$
  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
  It is straightforward (but laborious) to show that the pair
  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.

>>>>

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Geometration of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc}
\usepackage{manfnt}

@@

%% Global TikZ settings

\tikzset{every picture/.style={>=stealth}}

@@

\renewcommand{\bf}{\bar{f}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bm}{\bar{m}}
\newcommand{\bG}{\bar{G}}
\newcommand{\bH}{\bar{H}}
\newcommand{\tight}[3]{\hspace{-#1pt}{#2}\hspace{-#3pt}}
\newcommand{\GxG}{\text{$G \tight{1}{\times}{1} G$}}
\newcommand{\bGxG}{\text{$\bar{G} \tight{1}{\times}{1} \bar{G}$}}
\newcommand{\bfxf}{\text{$\bar{f} \tight{1}{\times}{1} \bar{f}$}}
\newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
\newcommand{\LxL}{\text{$\gcs{L} \tight{0}{\boxtimes}{0} \gcs{L}$}}
\newcommand{\ExE}{\text{$\cs{E}\tight{0}{\boxtimes}{0}\cs{E}$}}
\newcommand{\bExE}{\text{$\gcs{E}\tight{0}{\boxtimes}{0}\gcs{E}$}}
\newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
\newcommand{\BxB}{\text{$B \tight{1}{\times}{1} B$}}
\newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}

@@

  \[
  \xymatrix{
    \bm_3^*\gcs{L} \ar[rr]^{(\bm \tight{1}{\times}{2} \id)^*\mu} \ar[d]_{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]^{\id \boxtimes \mu}
    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
  }
  \]
  commutes, where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;

@@

  \[
  \xymatrix{
    \Frob_{\GxxG}^* \bm^* \gcs{L} \ar[rr]^{\Frob_{\GxxG}^*\mu}
    && \Frob_{\GxxG}^*(\LxL)\\
    \ar@{=}[u] \bm^*  \Frob_{G}^* \gcs{L} \ar[d]_{\bm^* F}
    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
    \bm^*\gcs{L} \ar[rr]^{\mu}
    && \LxL\\
  }
  \]
  commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such that
  \[
  \xymatrix{
  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
  && \LxL \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}\\
  }
  \]
  both commute.
\end{enumerate}

@@

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
determines a point $\bg$ on $\bG$ fixed by $\Frob_G$ and
therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically (this
follows from second condition appearing in the definition of character
sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
defined by $g \mapsto F_{\bg}$, is a group homomorphism;
we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
  $1$ local system. More generally, trace is needed.}

@@

  To see that $(\bfxf)^* \gcs{L}$ satisfies
  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$
  (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
  Then use the fact that $f$ is defined over $\Fq$, so
  $(\bfxf)^*\Frob_{\GxxG}^* \iso \Frob_{\GxxG} (\bfxf)^*$,
  and the fact that $f$ is a morphism of group schemes, so
  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
  (isomorphisms of functors on constructible sheaves).

  To see that $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
  $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
  above. It follows from the fact that sheaf hom commutes with these
  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

@@

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \tight{0}{\boxtimes}{0} \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  \Clifton{Agreed. I'll do that.}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

  Let us review how line bundles on $G^0$ determine character sheaves
  on $G^0$.  Up to isomorphism, line bundles on $G^0$ may be
  apprehended in terms of pairs $(\pi,\psi)$,
  \David{Aren't there line bundles which are not character sheaves,
    for which $B$ is not an algebraic group?}
  where $\pi : B\to G^0$ is a finite etale morphism of algebraic
  groups and a character $\psi : A\to \EEx$, where
  $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as
  summarized by the following diagram.
  \begin{equation}\label{E}
    \xymatrix{
      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
      }
  \end{equation}
  (In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the
  Lang isogeny for $G^0$.)  Indeed, $\cs{E}$ is precisely the
  component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$.  To
  see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back
  $\pi: B \to G^0$ along $m_0 : \GzxGz \to G^0$.
  \begin{equation}
    \xymatrix{
      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
      & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] \AxA  \ar[r]
      & \ar[u]^{m_{B}} \BxB \ar[r]^{\pi\tight{1}{\times}{1} \pi}  & \ar[u]^{m_0} \GzxGz \ar[r] & 1\\
      }
  \end{equation}
  As pictured above, the kernel of this pull-back is $\AxA$;
  indeed, $\AxA \to \BxB$ is the pull-back of $A\to B$ along
  $m_{B}$. Use this Cartesian square to define a character (the dotted
  arrow, above) of $\AxA$; that is, define $\AxA \to \EEx$
  by the composition of $\AxA \to A$ and $\psi : A\to \EEx$.
  Note that this character is $\psi \otimes \psi : \AxA \to \EEx$.
  \Clifton{I haven't explained how maps between diagrams define sheaf
    homomorphisms between local systems.}
  Since the lower sequence is precisely the sequence defining
  $\ExE$, this shows that, by construction, $\cs{E}$
  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \ExE$.
  Now the base change $\gcs{E}$ comes equipped with isomorphisms
  $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
  $\mu^0 : \bm_0^* \gcs{E} \to \bExE$
  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
  is a character sheaf of $G^0$.

@@

  Observe that $\bm: \bGxG \to \bG$ is
  completely determined by the family of maps
  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
  for all $x,y\in X$. To do that, note first that the local system
  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.

  \[
  \xymatrix{
    \EEx && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
    }
  \]
  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
  the result is the middle horizontal diagram below, where we use the
  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.

  \vspace{0.2in}

  \begin{tikzpicture}[auto,style={rectangle, scale=1.2}]
  \node (12) [anchor=east] at (4,2) {$\Aut(\bf^{x+y})$};
  \node (22) [anchor=west] at (4.4,2) {$\bH^{x+y}$};
  \node (32) [anchor=east] at (11,2) {$\bG^{x+y}$};
  \node (01) at (0,1) {$\EEx$};
  \node (11) [anchor=east] at (4,1) {$\Aut(\bf^{x+y})$};
  \node (21) [anchor=west] at (4.4,1) {$\bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y$};
  \node (31) [anchor=east] at (11,1) {$\bG^x\times \bG^y$};
  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
  \node (20) [anchor=west] at (4.4,0) {$\bG^x\times \bG^y$};
  \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
  \draw [->] (4.3,1.94) arc (330:30:0.12);
  \draw [->, densely dotted] (4.3,0.94) arc (330:30:0.12);
  \draw [->] (4.3,-0.06) arc (330:30:0.12);
  \draw [->] (12) to node[swap] {\footnotesize{$\psi_{x+y}$}} (01);
  \draw [->, densely dotted] (11) -- (01);
  \draw [->] (10) to node {\footnotesize{$\psi_x \otimes \psi_y$}} (01);
  \draw [->, densely dotted] ($(11.south) + (0,-0.5)$) -- (11);
  \draw [double equal sign distance] (11) -- (12);
  \draw [->] (22) to node {\footnotesize{$\bf^{x+y}$}} (32);
  \draw [->] ($(22.south) + (0,-0.5)$) -- (22);
  \draw [->] (21) -- (31);
  \draw [->] ($(32.south) + (0,-0.5)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32);
  \draw [->] ($(22.south) + (0,-1.5)$) -- ($(22.south) + (0,-1)$);
  \draw [->] (20) to node {\footnotesize{$\bf^x \times \bf^y$}} (30);
  \draw [->] ($(32.south) + (0,-1.5)$) -- ($(32.south) + (0,-1)$);
  \end{tikzpicture}

  \[
  \xymatrix{
    & \ar[dl]_{\psi_{x+y}} \Aut(\bf^{x+y})
    & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
    \EEx & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
    & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
    && \ar[u]_{\bm_{x,y}} \bG^x\times \bG^y\\
    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut(\bf^x)\times \Aut(\bf^y)
    & \ar@(ul,dl) & \ar[u] \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y}
    && \ar@{=}[u] \bG^x\times \bG^y\\
    }
  \]
  Now, the homomorphism from the covering group of
  $\bf^x\times\bf^y$ to the covering group of
  $\bf^{x+y}$ induced by the composition
  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
  Since this map commutes with the characters $\psi_x\otimes\psi_y$
  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
  It is straightforward (but laborious) to show that the pair
  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.
